Paper on the carbonate chemistry at Ny-Ålesund

### 2021-04-07 paper.Rmd
revised according to new variable names

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  dplyr::rename(pco2_contros = pco2_corr) %>% 
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

d_ts <- d %>%
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_contros,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

#sal_fb
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = 8)
ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
filename.html <- paste0(path_fig, "ts_sal_py.html")
saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")

>>>>

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  #dplyr::rename(pco2_contros = pco2_corr) %>% 
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

d_ts <- d %>%
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

#sal_fb
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = 8)
# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
# filename.html <- paste0(path_fig, "ts_sal_py.html")
# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
